Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-08-25 Latex/journal_v1/V5/pr.tex
change a bit latex

In figure \ref{fig:14}, the aggregate throughput is shown versus
the different number of UEs for a service with low interference for the IABV and FA methods in the feasible region.
The maximum power for each O-RU is 34dBm, and the maximum power for each UE is 30dBm. We assume that the system is not sensitive to fronhaul capacity and end-to-end delay and has enough VNF resources.
By increasing the number of UEs, the aggregate throughput raises.
And we can see that the IABV method is better than the FA method.

>>>>

In figure \ref{fig:14}, the aggregate throughput is shown versus
the different number of UEs for an eMBB service with low interference for the IABV and FA methods in the feasible region.
The minimum data rate for each UE is 1Mb/s/Hz.
The maximum power for each O-RU is 34dBm, and the maximum power for each UE is 30dBm. We assume that the system is not sensitive to fronhaul capacity and end-to-end delay and has enough VNF resources.
By increasing the number of UEs, the aggregate throughput raises.
And we can see that the IABV method is better than the FA method.
